---
title: "data"
format: html
editor: visual
---

# **Libraries**

In this section, we have loaded the libraries required for our project. The function of each library is specified below:

```{r}
library(readr)     # For data reading operations
library(readxl)    # For reading Excel files
library(utf8)      # For UTF-8 text processing
library(ggplot2)   # For data visualization
library(tidyverse) # For data manipulation and visualization
library(hrbrthemes) # Additional themes and theme components for ggplot2
library(ggthemes)  # Additional themes and color palettes for ggplot2
library(patchwork) # For combining ggplot2 graphics
library(tidyr)     # For data cleaning
library(openxlsx)  # For reading and writing Excel files
library(lubridate) # For date and time operations

```

# **Data Loading and Processing**

In this section, we loaded the datasets required for our project and processed the date information. The function of each code block is specified below:

```{r}
# We read the 'vendordatason.xlsx' file to create the 'fdatason' data frame.
fdatason <- read_excel("GitHub/emu430-fall2023-team-ctrl_s/vendordatason.xlsx")

# We read the 'new_data.xlsx' file to create the 'new_data' data frame.
new_data <- read_excel("GitHub/emu430-fall2023-team-ctrl_s/new_data.xlsx")

# We separated the 'Date' column into 'Year' and 'Month' columns.
new_data_sep_year <- new_data %>% separate(Date, c("Year","Month"), "-", remove = FALSE)

# We converted the dates in the 'Date' column to the year-month format.
new_data_sep_year$Date <- ym(new_data_sep_year$Date)
```

# \*\* Data Separation by Brand\*\*

In this section, we created separate data frames for each brand in our 'new_data_sep_year' data frame. This allows us to perform individual analyses for each brand. The code provided below is specific to Samsung, Apple, and Xiaomi. The same structure has been implemented for all other brands as well.

```{r}
# Creating a data frame for the Samsung brand
data_samsung <- new_data_sep_year %>% filter(Brand == "Samsung") 

# Creating a data frame for the Apple brand
data_apple <- new_data_sep_year %>% filter(Brand == "Apple")

# Creating a data frame for the Xiaomi brand
data_xiaomi <- new_data_sep_year %>% filter(Brand == "Xiaomi")

```

# \*\* Samsung's Global Dominance Graph\*\*

In this section, we created a graph using the dates and rates from our 'data_samsung' data frame. This graph illustrates Samsung's global dominance. The code structure used in this example has been repeated for all other brands as well.

```{r}
# Creating a graph with ggplot
glob_samsung_plot <- data_samsung %>% ggplot(aes(Date, Rate)) +
  geom_point(color = "black", size = 3) +  # Plotting points in black color with size 3
  theme_ipsum() +  # Using the 'ipsum' theme
  scale_y_continuous(limits = c(0, 60)) +  # Setting limits for the y-axis as 0 to 60
  ggtitle("Samsung's Global Dominance") +  # Setting the title of the graph
  scale_x_date(date_labels = "20%y-%m", date_breaks = "12 months") +  # Displaying dates on the x-axis in year-month format
  theme(axis.text.x = element_text(size = 26)) +  # Setting the size of text on the x-axis
  theme(axis.text.y = element_text(size = 29)) +  # Setting the size of text on the y-axis
  theme(plot.title = element_text(color = "#0c4da2", size = 48)) +  # Setting the color and size of the title text
  theme(axis.title.x = element_text(size = 30)) +  # Setting the size of the x-axis title
  theme(axis.title.y = element_text(size = 30)) +  # Setting the size of the y-axis title
  theme(panel.grid.major = element_line(size = 1.25),  # Setting the thickness of major grid lines
        panel.grid.minor = element_line(size = 1.00))  # Setting the thickness of minor grid lines

# Printing the graph
print(glob_samsung_plot)

```

# \*\* Turkish Market\*\*

In this section, we loaded the necessary datasets for the Turkish market and processed the date information. The function of each code block is specified below:

```{r}
# Reading the 'new_data_tr.xlsx' file to create the 'new_data_tr' data frame.
new_data_tr <- read_excel("GitHub/emu430-fall2023-team-ctrl_s/new_data_tr.xlsx")

# Separating the 'Date' column into 'Year' and 'Month' columns.
new_data_sep_year_tr <- new_data_tr %>% separate(Date, c("Year","Month"), "-", remove = FALSE)

# Converting the dates in the 'Date' column to the year-month format.
new_data_sep_year_tr$Date <- ym(new_data_sep_year_tr$Date)

```

# \*\* Brand-Based Data Separation for the Turkish Market\*\*

In this section, we created separate data frames for each brand in our 'new_data_sep_year_tr' data frame. This allows us to perform distinct analyses for each brand in the Turkish market. The code provided below is specific to Samsung, Apple, and Xiaomi. The same structure has been implemented for all other brands as well.

```{r}
# Creating a data frame for the Samsung brand in the Turkish market
data_samsung_tr <- new_data_sep_year_tr %>% filter(Brand == "Samsung")

# Creating a data frame for the Apple brand in the Turkish market
data_apple_tr <- new_data_sep_year_tr %>% filter(Brand == "Apple")

# Creating a data frame for the Xiaomi brand in the Turkish market
data_xiaomi_tr <- new_data_sep_year_tr %>% filter(Brand == "Xiaomi")
```

# \*\* Samsung's Dominance Graph in Turkey\*\*

In this section, we created a graph using the 'data_samsung_tr' data frame, showcasing the date and rates. This graph illustrates Samsung's dominance in the Turkish market. The code structure used in this example has been repeated for all other brands as well.

```{r}
# Creating a graph using ggplot
tr_samsung_plot <- data_samsung_tr %>% ggplot(aes(Date, Rate)) +
  geom_point(color = "black", size = 3) +  # Plotting points in black color with a size of 3
  theme_ipsum() +  # Using the 'ipsum' theme
  scale_y_continuous(limits = c(0, 60)) +  # Setting the limits of the y-axis to 0 and 60
  ggtitle("Samsung's Turkey Dominance") +  # Setting the title of the graph
  scale_x_date(date_labels = "20%y-%m", date_breaks = "12 months") +  # Displaying dates on the x-axis in year-month format
  theme(axis.text.x = element_text(size = 26)) +  # Setting the size of text on the x-axis
  theme(axis.text.y = element_text(size = 29)) +  # Setting the size of text on the y-axis
  theme(axis.title.x = element_text(size = 30)) +  # Setting the size of the x-axis title
  theme(axis.title.y = element_text(size = 30)) +  # Setting the size of the y-axis title
  theme(plot.title = element_text(color = "#0c4da2", size = 48)) +  # Setting the color and size of the title text
  theme(panel.grid.major = element_line(size = 1.25),  # Setting the thickness of major grid lines
        panel.grid.minor = element_line(size = 1.00))  # Setting the thickness of minor grid lines

# Printing the graph
print(tr_samsung_plot)

```

# \*\* Combining Graphs to Compare Samsung's Performance in Global and Turkish Markets\*\*

In this section, we combine two graphs to compare Samsung's performance in both the global and Turkish markets. The same structure has been implemented for all other brands as well.

```{r}
# Combining the graphs for Samsung's dominance in global and Turkish markets
samsung_compare_globtr <- tr_samsung_plot + glob_samsung_plot
print(samsung_compare_globtr)

# ----------------------------------------------------

# Combining the graphs for Apple's dominance in global and Turkish markets
apple_compare_globtr <- tr_apple_plot + glob_apple_plot
print(apple_compare_globtr)

# ----------------------------------------------------

# Combining the graphs for Xiaomi's dominance in global and Turkish markets
xiaomi_compare_globtr <- tr_xiaomi_plot + glob_xiaomi_plot
print(xiaomi_compare_globtr)
```

# **Creating a Comparison Graph for Multiple Brands in the Global Market**

In this section, we use ggplot to create a line graph that compares the performance of multiple brands (Samsung, Apple, Xiaomi, Huawei, Oppo) in the global market. The similar structure was used for the other two graphs, which involve 10 brands and 15 brands, respectively.

```{r}
# ggplot ile grafik oluşturma
compare_glob_five <- ggplot() +
  geom_line(data = data_samsung, aes(x = Date, y = Rate, color = "Samsung"), size = 2) +  # Drawing a line for Samsung
  geom_line(data = data_apple, aes(x = Date, y = Rate, color = "Apple"), size = 2) +  # Drawing a line for Apple
  geom_line(data = data_xiaomi, aes(x = Date, y = Rate, color = "Xiaomi"), size = 2) +  # Drawing a line for Xiaomi
  geom_line(data = data_huawei, aes(x = Date, y = Rate, color = "Huawei"), size = 2) +  # Drawing a line for Huawei
  geom_line(data = data_oppo, aes(x = Date, y = Rate, color = "Oppo"), size = 2) +  # Drawing a line for Oppo
  scale_x_date(date_labels = "20%y-%m", date_breaks = "12 months") +  # Displaying date labels on the X-axis in year-month format
  theme_ipsum() +  # Using the 'ipsum' theme
  scale_color_manual(values = c("Samsung" = "blue", "Apple" = "red",  # Setting colors for each brand's line
                                "Xiaomi" = "green", "Huawei" = "yellow", "Oppo" = "purple")) +
  labs(title = "Brands", color = "Brand") +  # Setting titles and color labels
  ggtitle("Global Market Percentages") +  # Setting the graph title
  theme(legend.text = element_text(size = 20)) +  # Setting the legend text size
  theme(axis.text.x = element_text(size = 26)) +  # Setting the X-axis text size
  theme(axis.text.y = element_text(size = 29)) +  # Setting the Y-axis text size
  theme(plot.title = element_text(color = "#0c4da2", size = 48)) +  # Setting the title text color and size
  theme(axis.title.x = element_text(size = 30)) +  # Setting the X-axis title size
  theme(axis.title.y = element_text(size = 30)) +  # Setting the Y-axis title size
  theme(panel.grid.major = element_line(size = 1.25),  # Setting the major grid line thickness
        panel.grid.minor = element_line(size = 1))  # Setting the minor grid line thickness
print(compare_glob_five)
```

# \*\* Creating a Comparison Graph for Multiple Brands in the Turkey Market\*\*

In this section, we use ggplot to create a line graph that compares the performance of multiple brands (Samsung, Apple, Xiaomi, Huawei, Oppo) in the Turkey market. The similar structure was used for the other two graphs, which involve 10 brands and 15 brands, respectively.

```{r}
# ggplot ile grafik oluşturma
compare_tr_five <- ggplot() +
  geom_line(data = data_samsung_tr, aes(x = Date, y = Rate, color = "Samsung"), size = 2) +  # Drawing a line for Samsung
  geom_line(data = data_apple_tr, aes(x = Date, y = Rate, color = "Apple"), size = 2) +  # Drawing a line for Apple
  geom_line(data = data_xiaomi_tr, aes(x = Date, y = Rate, color = "Xiaomi"), size = 2) +  # Drawing a line for Xiaomi
  geom_line(data = data_huawei_tr, aes(x = Date, y = Rate, color = "Huawei"), size = 2) +  # Drawing a line for Huawei
  geom_line(data = data_oppo_tr, aes(x = Date, y = Rate, color = "Oppo"), size = 2) +  # Drawing a line for Oppo
  scale_x_date(date_labels = "20%y-%m", date_breaks = "12 months") +  # Displaying date labels on the X-axis in year-month format
  theme_ipsum() +  # Using the 'ipsum' theme
  scale_color_manual(values = c("Samsung" = "blue", "Apple" = "red",  # Setting colors for each brand's line
                                "Xiaomi" = "green", "Huawei" = "yellow", "Oppo" = "purple")) +
  labs(title = "Brands", color = "Brand") +  # Setting titles and color labels
  ggtitle("Turkey Market Percentages") +  # Setting the graph title
  theme(legend.text = element_text(size = 20)) +  # Setting the legend text size
  theme(axis.text.x = element_text(size = 26)) +  # Setting the X-axis text size
  theme(axis.text.y = element_text(size = 29)) +  # Setting the Y-axis text size
  theme(plot.title = element_text(color = "#0c4da2", size = 48)) +  # Setting the title text color and size
  theme(axis.title.x = element_text(size = 30)) +  # Setting the X-axis title size
  theme(axis.title.y = element_text(size = 30)) +  # Setting the Y-axis title size
  theme(panel.grid.major = element_line(size = 1.25),  # Setting the major grid line thickness
        panel.grid.minor = element_line(size = 1))  # Setting the minor grid line thickness
print(compare_tr_five)
```
